---
title: "HAR Machine Learning Analysis"
output: html_document
---

In the initial setup, the seed is set so we can reproduce the results. Also the doParallel package is loaded for using the multiple cores while training. Caret and other required packages are loaded.

```{r}
set.seed(12345)
library(doParallel)
registerDoParallel(cores=4)
library(caret)
```

The training set is loaded and split up as the actual training and testing sets. Only the columns that have no NA's are used for model creation.

```{r}
training_orig<-read.csv("pml-training.csv")
testing_orig<-read.csv("pml-testing.csv")
inTrain<-createDataPartition(y=training_orig$classe, p=0.70,list=F)
training<-training_orig[inTrain,]
testing<-training_orig[-inTrain,]
cols<-c("roll_belt",
"pitch_belt",
"yaw_belt",
"total_accel_belt",
"gyros_belt_x",
"gyros_belt_y",
"gyros_belt_z",
"accel_belt_x",
"accel_belt_y",
"accel_belt_z",
"magnet_belt_x",
"magnet_belt_y",
"magnet_belt_z",
"roll_arm",
"pitch_arm",
"yaw_arm",
"total_accel_arm",
"gyros_arm_x",
"gyros_arm_y",
"gyros_arm_z",
"accel_arm_x",
"accel_arm_y",
"accel_arm_z",
"magnet_arm_x",
"magnet_arm_y",
"magnet_arm_z",
"roll_dumbbell",
"pitch_dumbbell",
"yaw_dumbbell",
"total_accel_dumbbell",
"gyros_dumbbell_x",
"gyros_dumbbell_y",
"gyros_dumbbell_z",
"accel_dumbbell_x",
"accel_dumbbell_y",
"accel_dumbbell_z",
"magnet_dumbbell_x",
"magnet_dumbbell_y",
"magnet_dumbbell_z",
"roll_forearm",
"pitch_forearm",
"yaw_forearm",
"total_accel_forearm",
"gyros_forearm_x",
"gyros_forearm_y",
"gyros_forearm_z",
"accel_forearm_x",
"accel_forearm_y",
"accel_forearm_z",
"magnet_forearm_x",
"magnet_forearm_y",
"magnet_forearm_z",
"classe")

model<-train(classe~.,data=training[,cols],method="rf", 
             trControl = trainControl(method="cv",number=4),
           preProcess = c("pca"))
```
Lets look at the model
```{r}
model
```
Predict the output of the testing data set and find out the accuracy using confusionMatrix function
```{r}
output<-predict(model,testing)
confusionMatrix(testing$classe,output)
```
Finally we test our model on the 20 observations that have been kept aside.
```{r}
predict(model,testing_orig)
```


